Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-28 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] removed all \christoph{...} and \fred{...} tags -> version for referee reply EPJC v2

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ when using
     measurements of only $F_H^\mu$, $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and finally allowing
     complex-valued new physics contributions to $\wilson{9,\,10}$. \checked{} %\fred{For 9,10,S,P,T,T5, the absolute value is in $[0.077,0.269] ([0.020, 0.379])$}
   }
\end{table*}

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
and \refsec{sec:scalar}---yields bounds very similar to those in
tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
are only small and in fact the bounds tend to be even more stringent
\fred{by $\sim (10 - 20) \%$} because tensor and scalar couplings can
contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
$\wilson{T,\, T5}$. This demonstrates that even in the case of
complex-valued couplings there is enough information in the data to
bound all 20 real and imaginary parts.

@@

For the \christoph{mass-eigenstate rate} asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
the nonvanishing width of the $B_s$ meson
(cf. \refapp{app:BKstarellell}), we find a rather uniform distribution
in scenarios with nonzero scalar couplings. So any value in the range
$[-1,\, 1]$ is plausible whereas {the SM and the scenario
  with only tensor couplings predict a value of precisely one
  \cite{DeBruyn:2012wk}}; cf. the last row in
\reftab{tab:postdictions}. Hence any deviation from one would
unambiguously hint at the presence of scalar operators.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself {constraints} on \fred{real and imaginary
    parts of the} tensor couplings \fred{$\wilson{T,\,T5}$} such that the
  upper bound of the smallest 68\% (95\%) credibility interval is
  \fred{$ \lesssim 0.25\, (0.45)$}, superseding previous bounds.  In
  combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  {predictions of} $B\to K^*$ form factors, the bounds are lowered to
  \fred{$\lesssim 0.23\, (0.39)$}, even in the presence of nonstandard
  contributions in vector couplings.
\item for the first time allows to {simultaneously} bound all four
  scalar couplings {$\wilson{S,S',P,P'}$} due to its complementarity
  to $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into
  account destructive interference with vector couplings, \fred{all
  credibility intervals contain the SM. The corresponding 1D intervals
  of real and imaginary parts have widths of $\sim 0.6\, (1.2)
  $ for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
  $\wilson{i} - \wilson{i'}$} for $i = S,P$. Currently, the bounds from
  $F_H^\mu$ are weaker than those from $\overline{\cal B}(B_s \to
  \bar\mu\mu)$ by about a factor of four. Future measurements of
  $F_H^\mu$ at LHCb and Belle II will further tighten the bounds.

@@

Our study of the {yet unmeasured} angular observables $J_{6c}$,
$(J_{1c} + J_{2c})$, and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
\bar\mu\mu$ (see \reftab{tab:postdictions}) shows that despite the
current bounds on tensor couplings, enhancements of up to two orders
of magnitude over the SM predictions are allowed for $(J_{1c} +
J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in reach of the LHCb
analysis of the full run~I data set. Our bounds on scalar couplings
from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
restrictive permitting only small deviations from SM predictions in
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the \christoph{
mass-eigenstate rate}
asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
couplings can take on any value in the range $[-1,\, 1]$.

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the plain branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s \christoph{\, A_{\Delta\Gamma}}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. \christoph{$A_{\Delta\Gamma}$ is the mass-eigenstate rate} asymmetry
due to nonvanishing width difference, which is \christoph{$A_{\Delta\Gamma} = 1$}
in the SM, but in general can be \christoph{$A_{\Delta\Gamma} \in [-1,\, 1]$}.
Since \christoph{$A_{\Delta\Gamma}$} can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.

>>>>

  \renewcommand{\arraystretch}{1.0}
  \caption{
     \label{tab:cTT5:1-dimCLs}
     The constraints on complex-valued $\wilson{T,\,T5}$ when using
     measurements of only $F_H^\mu$, $F_H^\mu$ and other data in
     \reftab{tab:observables} (except $\overline{\cal B}(B_s \to \bar\mu\mu)$), and finally allowing
     complex-valued new physics contributions to $\wilson{9,\,10}$.
  }
\end{table*}

@@

The most general fit of complex-valued tensor and scalar couplings
$\wilson{S,S',P,P',T,T5}$ in combination with vector couplings
$\wilson{9,\,9',\,10,\, 10'}$---the combination of \refsec{sec:tensor}
and \refsec{sec:scalar}---yields bounds very similar to those in
tables \ref{tab:cTT5:1-dimCLs} and~\ref{tab:cSP:1-dimCLs}. The changes
are only small and in fact the bounds tend to be even more stringent
by $\sim (10 - 20) \%$ because tensor and scalar couplings can
contribute to $F_H^{\mu}$ only constructively---see
\refeq{eq:FH-dependence}.  As before, branching-ratio measurements of
$B\to K^{*}\bar\mu\mu$ help to improve the constraints on
$\wilson{T,\, T5}$. This demonstrates that even in the case of
complex-valued couplings there is enough information in the data to
bound all 20 real and imaginary parts.

@@

For the mass-eigenstate rate asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by
the nonvanishing width of the $B_s$ meson
(cf. \refapp{app:BKstarellell}), we find a rather uniform distribution
in scenarios with nonzero scalar couplings. So any value in the range
$[-1,\, 1]$ is plausible whereas {the SM and the scenario
  with only tensor couplings predict a value of precisely one
  \cite{DeBruyn:2012wk}}; cf. the last row in
\reftab{tab:postdictions}. Hence any deviation from one would
unambiguously hint at the presence of scalar operators.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself {constraints} on real and imaginary
  parts of the tensor couplings $\wilson{T,\,T5}$ such that the
  upper bound of the smallest 68\% (95\%) credibility interval is
  $\lesssim 0.25\, (0.45)$, superseding previous bounds.  In
  combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  predictions of $B\to K^*$ form factors, the bounds are lowered to
  $\lesssim 0.23\, (0.39)$, even in the presence of nonstandard
  contributions in vector couplings.
\item for the first time allows to simultaneously bound all four
  scalar couplings $\wilson{S,S',P,P'}$ due to its complementarity
  to $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into
  account destructive interference with vector couplings, all
  credibility intervals contain the SM. The corresponding 1D intervals
  of real and imaginary parts have widths of $\sim 0.6\, (1.2)
  $for $\wilson{i} + \wilson{i'}$ and $\sim 0.15\, (0.3)$ for
  $\wilson{i} - \wilson{i'}$ for $i = S,P$. Currently, the bounds from
  $F_H^\mu$ are weaker than those from $\overline{\cal B}(B_s \to
  \bar\mu\mu)$ by about a factor of four. Future measurements of
  $F_H^\mu$ at LHCb and Belle II will further tighten the bounds.

@@

Our study of the {yet unmeasured} angular observables $J_{6c}$,
$(J_{1c} + J_{2c})$, and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi)
\bar\mu\mu$ (see \reftab{tab:postdictions}) shows that despite the
current bounds on tensor couplings, enhancements of up to two orders
of magnitude over the SM predictions are allowed for $(J_{1c} +
J_{2c})$ and $(J_{1s} - 3 J_{2s})$, placing them in reach of the LHCb
analysis of the full run~I data set. Our bounds on scalar couplings
from $B_s\to \bar\mu\mu$ and $F_H^\mu$, however, are already quite
restrictive permitting only small deviations from SM predictions in
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the mass-eigenstate
rate asymmetry $A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ given nonzero scalar
couplings can take on any value in the range $[-1,\, 1]$.

@@

  Concerning $B_s\to \bar\ell\ell$, the expression \refeq{eq:Br-Bsmumu:time0}
  corresponds to the plain branching ratio at time $t=0$. Due to the
  nonvanishing decay width $\Delta\Gamma_s$, experiments measure the average
  time-integrated branching ratio---denoted by $\overline{\cal B}$---and the two
  are related as \cite{DeBruyn:2012wk}
\begin{align}
  \label{eq:Br-Bsmumu}
  \overline{\cal B} (B_s \to \bar\ell\ell) &
  = \frac{1 + y_s \, A_{\Delta\Gamma}}{1 - y_s^2} {\cal B} (B_s \to \bar\ell\ell)\,.
\end{align}
Here $y_s \equiv \Delta\Gamma_s/(2\Gamma_s)$ with the numerical value given in
\cite{Beaujean:2013soa}. $A_{\Delta\Gamma}$ is the mass-eigenstate rate asymmetry
due to nonvanishing width difference, which is $A_{\Delta\Gamma} = 1$
in the SM, but in general can be $A_{\Delta\Gamma} \in [-1,\, 1]$.
Since $A_{\Delta\Gamma}$ can depart from it's SM value in scenarios of
new physics considered in this work, we take this effect into account
in our numerical analysis, although it is suppressed by small $y_s$. The latest
SM prediction $\overline{\cal B} (B_s \to \bar\mu\mu) = (3.65 \pm 0.23) \cdot
10^{-9}$~\cite{Bobeth:2013uxa} includes NLO electroweak \cite{Bobeth:2013tba}
and NNLO QCD corrections \cite{Hermann:2013kca}.
